Visitation_stacked_barplot

### 2020-12-01 Rmd/Visitation_stacked_barplot.Rmd
organising clusters

p<- ggplot(net_long_1) +
  aes(x = reorder(Id,-order), 
      y = measurement, 
      fill =factor(orders, levels=c("Hemiptera","Coleoptera","Lepidoptera","Diptera", "Hymenoptera"))) +
  geom_bar(position = "fill", stat = "identity", alpha=0.6) +coord_flip() +scale_x_discrete(labels= la) + 
  scale_fill_manual(legend_title,values=c("indianred", "gray49", "seagreen", "darkgoldenrod2", "#386cb0")) + theme_classic()+xlab("Networks")+ylab("Percentage of visits") +scale_y_continuous(labels = scales::percent) + theme(legend.background = element_rect(fill=alpha('blue', 0.0)))+
  annotation_custom(l, xmin = 9.365, xmax = 10.0, ymin = 1.03, ymax =1.09) + annotation_custom(bumb, xmin = 7.1, xmax = 9.3, ymin = 1.03, ymax =1.09)+ annotation_custom(dip, xmin = 8.65, xmax = 9.25, ymin = 1.035, ymax =1.085)+
  coord_cartesian(clip = "off") + annotation_custom(beet, xmin = 9.96, xmax = 10.76, ymin = 0.86, ymax =1.255)+ annotation_custom(hem, xmin = 10.86, xmax = 11.36, ymin = 0.883, ymax =1.233)+
  coord_cartesian(clip = "off")+ coord_flip()

>>>>

p<- ggplot(net_long_1) +
  aes(x = reorder(Id,-order), 
      y = measurement, 
      fill =factor(orders, levels=c("Hemiptera","Coleoptera","Lepidoptera","Diptera", "Hymenoptera"))) +
  geom_bar(position = "fill", stat = "identity", alpha=0.6) +coord_flip() +scale_x_discrete(labels= la) + 
  scale_fill_manual(legend_title,values=c("indianred", "gray49", "seagreen", "darkgoldenrod2", "#386cb0")) + theme_classic()+xlab("Networks")+ylab("Percentage of visits") +scale_y_continuous(labels = scales::percent) + theme(legend.background = element_rect(fill=alpha('blue', 0.0)))+
  annotation_custom(l, xmin = 9.365, xmax = 10.0, ymin = 1.03, ymax =1.09) + annotation_custom(bumb, xmin = 7.1, xmax = 9.3, ymin = 1.03, ymax =1.09)+ annotation_custom(dip, xmin = 8.65, xmax = 9.25, ymin = 1.035, ymax =1.085)+
  coord_cartesian(clip = "off") + annotation_custom(beet, xmin = 9.96, xmax = 10.76, ymin = 0.86, ymax =1.255)+ annotation_custom(hem, xmin = 10.86, xmax = 11.36, ymin = 0.883, ymax =1.233)+
  coord_cartesian(clip = "off")+ coord_flip()+coord_cartesian(clip = "off")

### 2020-12-01 Scripts/6_Plot/6_Model_output_plot.Rmd
organising clusters

---
title: "Visitation_stacked_barplot"
output:
  pdf_document: default
  html_document: default
---

@@

# 
d_1 <- get_png("Images/dip_green_2.png")
l <- get_png("Images/lepi_brown.png")
b <- get_png("Images/bee_orange.png")
f <- get_png("Images/form_2.png")
s <- get_png("Images/syr_blue.png")

t <- grid::roundrectGrob(x=10, y=10, width=10, height=10)

t <- ggplot(ce_1[[1]], aes(x = Clusters, y = Interaction, colour = as.factor(guild), group = 
  as.factor(guild))) +
  geom_point(size = 1.2, position = position_dodge(width = 0.9), alpha=1) +
  theme_bw()+ ylab("Nº of visits per plant taxa") + xlab("Plant reproductive groups")+
  geom_point(data = d_5_1,aes(x = Clusters, y = (Interaction+1)),size = 1.2, position = position_jitterdodge(dodge.width = 0.9,   jitter.width = 0.2), alpha=0.2)+
  geom_errorbar(data=ce_1[[1]],mapping=aes(x=Clusters, ymin=lower__, ymax=upper__,colour = as.factor(guild), group = 
  as.factor(guild)), width=.6,alpha=0.85, size = 0.9,position = position_dodge(width = 0.9)) +ylim(0,200)+
  scale_color_manual("Floral visitors guilds",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black"))+  theme(panel.grid.major.x = element_blank(),panel.grid.minor.y  = element_blank())+   geom_vline(xintercept = c(1.5,2.5,3.5,4.5), linetype="dashed", color = "black", size=0.5)

t_1 <-  t + annotation_custom(l, xmin = 1.17, xmax =1.28 , ymin = -5.5, ymax =-0.5)+
  annotation_custom(l, xmin = 1.17, xmax =1.28 , ymin = -5.75, ymax =-0.5) +  
  annotation_custom(b, xmin = 0.55, xmax =0.70 , ymin = -5, ymax =0) + 
 annotation_custom(f, xmin = 0.67, xmax =0.87 , ymin = -4.5, ymax =-0.65) + 
 annotation_custom(s, xmin = 0.85, xmax =0.99 , ymin = -5.5, ymax =-0.25)+
  annotation_custom(d_1, xmin = 1.0, xmax =1.14 , ymin = -5, ymax =0)

gg_table <- ggplot_gtable(ggplot_build(t_1))
gg_table$layout$clip[gg_table$layout$name=="panel"] <- "off"
grid.draw(gg_table)

>>>>

---
title: ""
output:
  pdf_document: default
  html_document: default
---

@@

# 
d_1 <- get_png("Images/dip_green_2.png")
l <- get_png("Images/lepi_brown.png")
b <- get_png("Images/bee_orange.png")
f <- get_png("Images/form_2.png")
s <- get_png("Images/syr_blue.png")
beet <- get_png("Images/beet_black.png")

t <- grid::roundrectGrob(x=20, y=20, width=20, height=20)

t <- ggplot(ce_1[[1]], aes(x = Clusters, y = Interaction, colour = as.factor(guild), group = 
  as.factor(guild))) +
  geom_point(size = 1.2, position = position_dodge(width = 0.9), alpha=1) +
  theme_bw()+ ylab("Nº of visits per plant taxa") + xlab("Plant reproductive groups")+
  geom_point(data = d_5_1,aes(x = Clusters, y = (Interaction+1)),size = 1.2, position = position_jitterdodge(dodge.width = 0.9,   jitter.width = 0.2), alpha=0.2)+
  geom_errorbar(data=ce_1[[1]],mapping=aes(x=Clusters, ymin=lower__, ymax=upper__,colour = as.factor(guild), group = 
  as.factor(guild)), width=.6,alpha=0.85, size = 0.9,position = position_dodge(width = 0.9)) +ylim(0,200)+
  scale_color_manual("Floral visitors guilds",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black"))+  theme(panel.grid.major.x = element_blank(),panel.grid.minor.y  = element_blank())+   geom_vline(xintercept = c(1.5,2.5,3.5,4.5), linetype="dashed", color = "black", size=0.5)+coord_cartesian(clip = "off")+theme(legend.box.margin=margin(6,6,6,6))
  #cluster 1
t_1 <-  t + annotation_custom(l, xmin = 1.17, xmax =1.28 , ymin = -5.75, ymax =0.5)+ #needed to colour the rest
  annotation_custom(l, xmin = 1.17, xmax =1.28 , ymin = -5.75, ymax =0.5) +  #lepidoptera
  annotation_custom(b, xmin = 0.55, xmax =0.70 , ymin = -5, ymax =0) + #bee
  annotation_custom(f, xmin = 0.67, xmax =0.87 , ymin = -4.5, ymax =-0.65) + #wasp
  annotation_custom(s, xmin = 0.85, xmax =0.99 , ymin = -5.5, ymax =-0.25)+ # syrphid
  annotation_custom(d_1, xmin = 1.0, xmax =1.14 , ymin = -5.75, ymax =1) + #diptera
  annotation_custom(beet, xmin = 1.265, xmax =1.485 , ymin = -4.5, ymax =-0.35) #beetle
  #cluster 2
t_2 <-  t_1 + annotation_custom(l, xmin = 2.17, xmax =2.28 , ymin = -5.75, ymax =0.5)+ #needed to colour the rest
  annotation_custom(l, xmin = 2.17, xmax =2.28 , ymin = -5.75, ymax =0.5) +  #lepidoptera
  annotation_custom(b, xmin = 1.55, xmax =1.70 , ymin = -5, ymax =0) + #bee
  annotation_custom(f, xmin = 1.67, xmax =1.87 , ymin = -4.5, ymax =-0.65) + #wasp
  annotation_custom(s, xmin = 1.85, xmax =1.99 , ymin = -5.5, ymax =-0.25)+ # syrphid
  annotation_custom(d_1, xmin = 2.0, xmax =2.14 , ymin = -5.75, ymax =1) + #diptera
  annotation_custom(beet, xmin = 2.265, xmax =2.485 , ymin = -4.5, ymax =-0.35) #beetle
  #cluster 3
t_3 <-  t_2 + annotation_custom(l, xmin = 3.17, xmax =3.28 , ymin = -5.75, ymax =0.5)+ #needed to colour the rest
  annotation_custom(l, xmin = 3.17, xmax =3.28 , ymin = -5.75, ymax =0.5) +  #lepidoptera
  annotation_custom(b, xmin = 2.55, xmax =2.70 , ymin = -5, ymax =0) + #bee
  annotation_custom(f, xmin = 2.67, xmax =2.87 , ymin = -4.5, ymax =-0.65) + #wasp
  annotation_custom(s, xmin = 2.85, xmax =2.99 , ymin = -5.5, ymax =-0.25)+ # syrphid
  annotation_custom(d_1, xmin = 3.0, xmax =3.14 , ymin = -5.75, ymax =1) + #diptera
  annotation_custom(beet, xmin = 3.265, xmax =3.485 , ymin = -4.5, ymax =-0.35) #beetle
  #cluster 4
t_4 <-  t_3 + annotation_custom(l, xmin = 4.17, xmax =4.28 , ymin = -5.75, ymax =0.5)+ #needed to colour the rest
  annotation_custom(l, xmin = 4.17, xmax =4.28 , ymin = -5.75, ymax =0.5) +  #lepidoptera
  annotation_custom(b, xmin = 3.55, xmax =3.70 , ymin = -5, ymax =0) + #bee
  annotation_custom(f, xmin = 3.67, xmax =3.87 , ymin = -4.5, ymax =-0.65) + #wasp
  annotation_custom(s, xmin = 3.85, xmax =3.99 , ymin = -5.5, ymax =-0.25)+ # syrphid
  annotation_custom(d_1, xmin = 4.0, xmax =4.14 , ymin = -5.75, ymax =1) + #diptera
  annotation_custom(beet, xmin = 4.265, xmax =4.485 , ymin = -4.5, ymax =-0.35) #beetle
  #cluster 5
t_5 <-  t_4 + annotation_custom(l, xmin = 5.17, xmax =5.28 , ymin = -5.75, ymax =0.5)+ #needed to colour the rest
  annotation_custom(l, xmin = 5.17, xmax =5.28 , ymin = -5.75, ymax =0.5) +  #lepidoptera
  annotation_custom(b, xmin = 4.55, xmax =4.70 , ymin = -5, ymax =0) + #bee
  annotation_custom(f, xmin = 4.67, xmax =4.87 , ymin = -4.5, ymax =-0.65) + #wasp
  annotation_custom(s, xmin = 4.85, xmax =4.99 , ymin = -5.5, ymax =-0.25)+ # syrphid
  annotation_custom(d_1, xmin = 5.0, xmax =5.14 , ymin = -5.75, ymax =1) + #diptera
  annotation_custom(beet, xmin = 5.265, xmax =5.485 , ymin = -4.5, ymax =-0.35) #beetle
  #legend
t_6 <-  t_5 + annotation_custom(l, xmin = 5.65, xmax =5.76 , ymin = 84.4, ymax =90.8)+ #lepidoptera
              annotation_custom(b, xmin = 5.65, xmax =5.76 , ymin = 108, ymax =117.5)+ #bee
              annotation_custom(f, xmin = 5.65, xmax =5.76 , ymin = 105, ymax =108.5)+ #wasp
              annotation_custom(s, xmin = 5.65, xmax =5.76 , ymin = 97.5, ymax =102.5)+ #syrphid
              annotation_custom(d_1, xmin = 5.65, xmax =5.76 , ymin = 89, ymax =99) + #diptera
              annotation_custom(beet, xmin = 5.65, xmax =5.76 , ymin = 79.5, ymax =83.5) #beetle

gg_table <- ggplot_gtable(ggplot_build(t_6))
gg_table$layout$clip[gg_table$layout$name=="panel"] <- "off"
grid.draw(gg_table)
